\thetitle

### 2021-05-19 writing/results.tex
moving broken wrap figure
Update plots and discussion of results with new data from re-run

\begin{figure} \footnotesize 
  \centering
  \includegraphics[width=\textwidth]{./plots/avo-bars}

@@

     Each diagram shows the overlap of the successful scenarios for three modes.
     For example, in the leftmost diagram, all three modes succeed on the same
     scenario 57.3\% of the time, only Natural and Natural exceptions succeed on
     29.1\% of the scenarios, only Natural and Erasure succeed on 2.1\%, and
     Natural alone succeeds on 9\%.  \\ The upper bound margin of error is 0.02\%.

@@

The second key observation from figure~\ref{fig:success-bars} is that the
modes that use blame all outperform those that do not.  In particular,
Natural and both of Transient's blame modes succeed in around 95\% of the
scenarios, while their corresponding exception modes succeed in around
85\% of them, and Erasure succeeds in only 60\%.  The only
exception is that the random programmer always succeeds; this reflects the
fact that every scenario has finitely many modules, so the random programmer 
eventually types the buggy module.

Figure~\ref{fig:avo-bars} depicts a head-to-head comparison of every
mode's performance against every other mode (except Random). The
comparison  answers the four questions from section~\ref{sub:experiment}. 
Each plot shows the proportion of scenarios where one mode performs
better or worse than each other mode.  In particular, each bar above zero
represents the proportion where the plot's named mode succeeds and the
mode on the x-axis fails; the corresponding bar below zero represents the
proportion of the inverse case.  For example, the plot titled ``Natural''
shows that Natural outperforms Natural exceptions in about 12\% of the
scenarios, and the inverse (Natural performs worse than Natural
exceptions) never happens.  Similarly, the plot titled ``Transient last
blame'' shows that Transient last blame outperforms Natural exceptions
 in about 12\% of the scenarios, but conversely it performs worse
than Natural exceptions in about 2\% of the scenarios.

The figure answers questions $Q_1$, $Q_2$ and $Q_3$ affirmatively.  
In all three semantics, blame modes outperform their
corresponding exception mode by \textasciitilde10\%.  The
Natural exceptions mode is never more useful than Natural blame, and
Transient exceptions are more useful than Transient first and Transient
last blame in a small percentage (about 2\%) of the scenarios.

Figure~\ref{fig:avo-bars} also provides answers for $Q_*$.
Blame for all three semantics is significantly
more useful than Erasure exceptions (by around 35\%). Natural blame is
more useful than both versions of Transient blame by a small percentage;
in about 4\% of scenarios Natural blame is more useful while in about 1.5\% of the
scenarios Transient blame is more useful. The Transient first and
Transient last blame are practically indistinguishable. Finally, there is
no clear winner between Natural exceptions and Transient exceptions
despite the theoretically advantageous additional checks of Natural.

@@

  \vspace{1em}
  \begin{minipage}{0.95\textwidth}
    Each plot depicts the distribution of trail lengths for a given mode across all benchmarks.
  \end{minipage}

@@

    Each plot depicts the distribution of scenarios with trail length
    differences ranging from -3 to 3.  A -x difference denotes that the first
    mode's trail is x steps {\em shorter\/} than the second mode's trail for the
    same scenario; a positive difference denotes the inverse.  Only
    scenarios where both modes succeed are considered.  The 10|85 on the y-axis
    indicates that the axis is truncated between 10 and 85\%.

@@

An alternative way to understand the answers for questions $Q_1$ to $Q_3$, is to
analyze the success of each semantics in comparison to
Erasure. Figure~\ref{fig:success-venns} depicts the results of this analysis.
Specifically, the figure shows one Venn diagram per mode of the rational
programmer that uses blame.  Each diagram shows the overlap of successful
scenarios for the blame mode, its corresponding exception mode, and Erasure.
For example, the leftmost diagram (Natural) shows that all three modes succeed
on 59.5\% of the scenarios, only Natural and Natural exceptions succeed on
25.7\% of the scenarios, only Natural and Erasure succeed on 2.1\%, and Natural
alone succeeds on 9.7\%.  This analysis highlights the success trade-offs each
semantics offers against Erasure, with and without blame. For instance, the
analysis for Natural clearly illustrates that, when choosing between Natural
blame, Natural exceptions, and Erasure, Natural blame is the absolutely most
successful: all of the successes of the other two modes are subsets of Natural's
successful scenarios.  On the other hand, Transient's blame modes fare similarly
but the choice is not so clear-cut.

Turning to programmer effort, figure~\ref{fig:effort-table} shows the
distribution of blame trail lengths for the sampled interesting debugging
scenarios. Unlike the usefulness comparisons above, these proportions do
not generalize to a representation of the full population.  Still, as
section~\ref{subsec:effort} discusses, they provide an alternative view of
the workings of the rational programmer.

There are two immediate take-aways from the figure. First, the effort for
successfully debugging interesting scenarios (in green) for the random
mode of the rational programmer is highly spread out, as
expected. In contrast, in the other modes, successful effort coalesces at
the left side of the plot, meaning that in most cases the programmer needs
to type a single module to debug a scenario.

@@

Figure~\ref{fig:effort-comparisons} provides head-to-head comparisons of
effort.  The comparison between two modes boils down to the difference in
length between their trails for all scenarios where they both succeed.
Hence, each plot in the figure shows the distribution of scenarios with
length differences ranging from -3 (the first mode's trail is 3 steps
shorter than the second's) to 3 (the first mode's trail is 3 steps longer
than the second's).  The figure offers several insights about how  modes
compare in terms of effort that complement the insights about how they
compare in terms of success rates from figure~\ref{fig:avo-bars}.  First,
Natural blame never produces shorter trails than Natural exceptions, and
sometimes (albeit rarely) produces slightly longer ones.  Hence, the
experiment provides evidence that blame helps the rational programmer
debug more scenarios but does not shorten the debugging process compared
to exceptions. Second, Natural relatively often (around 10\% of the
scenarios) produces shorter trails than both Transient blame modes, and
sometimes the trails are significantly shorter.  Third, Transient last
blame often produces shorter trails than Transient first blame, which is a
particularly interesting distinction in light of their nearly
indistinguishable success rates.  Finally, Transient's blame modes also
share the characteristic with Natural that blame sometimes produces longer
trails than their corresponding exception modes.

>>>>

\
\begin{figure} \footnotesize 
  \centering
  \includegraphics[width=\textwidth]{./plots/avo-bars}

@@

     Each diagram shows the overlap of the successful scenarios for three modes.
     For example, in the leftmost diagram, all three modes succeed on the same
     scenario 57.3\% of the time, only Natural and Natural exceptions succeed on
     29.1\% of the scenarios, only Natural and Erasure succeed on 2.1\%, and
     Natural alone succeeds on 9\%. The upper bound margin of error is 0.02\%.

@@

The second key observation from figure~\ref{fig:success-bars} is that the modes
that use blame all outperform those that do not. In particular, Natural and both
of Transient's blame modes succeed in 85 - 90\% of the scenarios, while their
corresponding exception modes succeed in less than 80\% of them, and so too for
Erasure. The only exception is that the random programmer always succeeds; the
figure omits this mode because it just reflects the fact that every scenario has
finitely many modules, so the random programmer eventually types the buggy
module.

Figure~\ref{fig:avo-bars} depicts a head-to-head comparison of every
mode's performance against every other mode (except Random). The
comparison  answers the four questions from section~\ref{sub:experiment}. 
Each plot shows the proportion of scenarios where one mode performs
better or worse than each other mode.  In particular, each bar above zero
represents the proportion where the plot's named mode succeeds and the
mode on the x-axis fails; the corresponding bar below zero represents the
proportion of the inverse case.  For example, the plot titled ``Natural''
shows that Natural outperforms Natural exceptions in about 11\% of the
scenarios, and the inverse (Natural performs worse than Natural
exceptions) never happens.  Similarly, the plot titled ``Transient last
blame'' shows that Transient last blame outperforms Natural exceptions
 in about 9\% of the scenarios, but conversely it performs worse
than Natural exceptions in about 2\% of the scenarios.

The figure answers questions $Q_1$, $Q_2$ and $Q_3$ affirmatively.  
In all three semantics, blame modes outperform their
corresponding exception mode by \textasciitilde10\%.  The
Natural exceptions mode is never more useful than Natural blame, and
Transient exceptions are more useful than Transient first and Transient
last blame in a small percentage (less than 1\%) of the scenarios.

Figure~\ref{fig:avo-bars} also provides answers for $Q_*$. Blame for all three
semantics is significantly more useful than Erasure exceptions --- by almost
12\% for Natural and almost 9\% for Transient. Natural blame is more useful than
both versions of Transient blame by a small percentage (about 4\%). The
Transient first and Transient last blame are practically indistinguishable.
Finally, Natural exceptions are more useful than Transient exceptions, although
only in a small percentage of scenarios (about 2.5\%). A rare few scenarios
(about 0.5\%) show the opposite, despite the theoretically advantageous
additional checks of Natural.

@@

  \vspace{1em}
  \begin{minipage}{0.95\textwidth}
    Each plot depicts the distribution of trail lengths for a given mode across all benchmarks.
    The upper bound margin of error is 0.05\%.
  \end{minipage}

@@

    Each plot depicts the distribution of scenarios with trail length
    differences ranging from -3 to 3. A $-x$ difference denotes that the first
    mode's trail is $x$ steps {\em shorter\/} than the second mode's trail for the
    same scenario; a positive difference denotes the inverse. A difference of
    $\infty$ indicates one mode's trail succeeds while other mode's fails. The
    15|60 on the y-axis indicates that the axis is truncated between 15 and
    60\%.
    The upper bound margin of error is 0.03\%.

@@

An alternative way to understand the answers for questions $Q_1$ to $Q_3$, is to
analyze the success of each semantics in comparison to
Erasure. Figure~\ref{fig:success-venns} depicts the results of this analysis.
Specifically, the figure shows one Venn diagram per mode of the rational
programmer that uses blame.  Each diagram shows the overlap of successful
scenarios for the blame mode, its corresponding exception mode, and Erasure.
For example, the leftmost diagram (Natural) shows that all three modes succeed
on 75.7\% of the scenarios, only Natural and Natural exceptions succeed on
11.6\% of the scenarios, only Natural and Erasure succeed on 1.8\%, and Natural
alone succeeds on 9.2\%.  This analysis highlights the success trade-offs each
semantics offers against Erasure, with and without blame. For instance, the
analysis for Natural clearly illustrates that, when choosing between Natural
blame, Natural exceptions, and Erasure, Natural blame is the absolutely most
successful: all of the successes of the other two modes are subsets of Natural's
successful scenarios.  On the other hand, Transient's blame modes fare similarly
but the choice is not so clear-cut.

Turning to programmer effort, figure~\ref{fig:effort-table} shows the
estimated distribution of blame trail lengths for the interesting debugging
scenarios. There are two immediate take-aways from the figure. First, the effort for
successfully debugging interesting scenarios (in green) for the random
mode of the rational programmer is highly spread out, as
expected. In contrast, in the other modes, successful effort coalesces at
the left side of the plot, meaning that in most cases the programmer needs
to type a single module to debug a scenario.

@@

Figure~\ref{fig:effort-comparisons} provides head-to-head comparisons of effort.
The comparison between two modes boils down to the difference in length between
their trails for all scenarios where they both succeed. Hence, each plot in the
figure shows the distribution of scenarios with length differences ranging from
-3 (the first mode's trail is 3 steps shorter than the second's) to 3 (the first
mode's trail is 3 steps longer than the second's). The figure offers several
insights about how modes compare in terms of effort that complement the insights
about how they compare in terms of success rates from figure~\ref{fig:avo-bars}.
First, Natural blame never produces shorter trails than Natural exceptions, and
sometimes (albeit rarely) produces slightly longer ones. Hence, the experiment
provides evidence that blame helps the rational programmer debug more scenarios
but does not shorten the debugging process compared to exceptions. Second,
Natural relatively often (close to 8\% of the scenarios) produces shorter trails
than both Transient blame modes, and sometimes the trails are significantly
shorter. Finally, Transient's blame modes also share the characteristic with
Natural that blame sometimes produces longer trails than their corresponding
exception modes.
